---
title: "Report 1"
metadata-files:
  - _metadata.yml
format: pdf
---

```{r echo = FALSE}
#| include: false
library(tidyverse)
library(targets)
library(modelsummary)
library(kableExtra)
library(haven)
```

This is Report 1, which has information about the data used in the model estimations as well as the estimations for the work from home model, the telecommuting frequency model, and the auto ownership mode.
In addition, there is an update on the highway network.

# Data

We used data from both the National Household Travel Survey and the Utah Household Travel Survey in our analysis.

## The National Household Travel Survey

The National Household Travel Survey (NHTS) is a periodic survey conducted by the Federal Highways Administration (FHWA).
It collects data on the travel behavior and patterns of households and individuals in the United States.
Participants answer questions about how they travel, the modes of transportation they use, the reasons for their trips, and various demographic and socioeconomic factors that influence travel behavior including household size and income.
The survey responses are labeled by region and MSA categorization.
In this case, we chose to use all responses of people in MSAs with less than one million people, since this category closely lines up with Logan, UT.

The household income was split into eleven different categories.
@fig-orig shows what the income data looked like originally.

```{r, echo = FALSE}
#| label: fig-orig
#| tbl-cap: Original income distributions

tar_load(nhts)

ggplot(nhts$per, aes(x = HHFAMINC)) +
	geom_bar(fill = "pink", color = "black") +
	labs(title = "Bar Chart of Household Income",
			 x = "Household Income Categories",
			 y = "Frequency") +
	theme_bw()
```

We grouped the income levels into smaller categories, so that instead of having eleven groups, there were four groups.
The category breakdowns are from 1) less than \$10,000 to \$49,999, 2) from \$50,000 to \$99,999, 3) from \$100,000 to \$149,999, and 4) from \$150,000 and up.
@fig-new shows the new distribution of income levels.

```{r echo = FALSE}
#| label: fig-new
#| tbl-cap: New income distributions (grouped)

clean_income <- nhts$per %>% 
	mutate(
		HHFAMINC_cat = recode(
			HHFAMINC,
			"01" = "1", "02" = "1", "03" = "1", "04" = "1", "05" = "1",
			"06" = "2", "07" = "2",
			"08" = "3", "09" = "3",
			"10" = "4", "11" = "4"
			)) %>% 
	filter(HHFAMINC_cat > 0)

ggplot(clean_income, aes(x = HHFAMINC_cat)) +
	geom_bar(fill = "pink", color = "black") +
	labs(title = "Bar Chart of Household Income",
			 x = "Household Income Categories",
			 y = "Frequency") +
	theme_bw()
```

We also used the life cycle of the household which describes the demographic makeup of the household describing combinations of adults and children of different ages.
We used three different categories: 1) one adult with children 0-5, 2) two or more adults with children 0-5 and 3) any other life cycle category.

We categorized the number of vehicles by labeling any household that has three or more vehicles as just having three vehicles.

## The Utah Household Travel Survey

The Utah Household Travel Survey (UHTS) is similar to the NHTS, but it is specific to the state of Utah.
This survey also gathers information about people's travel patterns as well as their demographic and socioeconomic information.
They survey responses are labeled by county.
In this case, we chose to use all responses of people located in Cache County, UT because Logan is located in Cache County.

# Model Estimations

We estimated coefficients for the work from home model, the telecommuting frequency model, and the auto ownership model.

## Work From Home

The work from home (WFH) model is designed to analyze and predict the likelihood or factors influencing the choice of individuals to work from home.

We modeled the WFH model for Logan after the WFH model in the SEMCOG model.
The SEMCOG model used variables such as worker status, gender, education level, household incomes, and age groups.

In our model for Logan, UT, we included a variety of alternative specific variables.
We included the life cycle of the household because individuals with young children may prefer to work from home.
We also included the number of vehicles because the number of vehicles in a household may impact the ability of people in the household to commute which may impact the likelihood of working from home.
Income level was also included because the income of a person may affect their ability to have a home office and jobs in certain salary brackets may be more or less likely to have work from home options.
The final variable we included was the sex of the respondent because sex may also play a role in work location choices.

With these variables, we created several multinomial logit models because there are multiple categories of work locations (@tbl-wfh).
The "life cycle" variable is not significant in any of these models.
We will use Model 4 due to its exclusion of "life cycle" and its inclusion of all other variables, many of which are statistically significant.

```{r echo = FALSE}
#| label: tbl-wfh
#| tbl-cap: Work-from-home model estimates

modelsummary(
		tar_read(wfh_models),
		estimate = "{estimate} ({p.value}){stars}",
		statistic = NULL,
		gof_omit = "r2|Num"
	) %>% 
	kable_styling(latex_options = "scale_down")
```

## Telecommuting Frequency

The telecommuting frequency model is designed to analyze and predict how often an individual engages in telecommuting or remote work.
Since the COVID-19 pandemic in 2020, there has been an increase in the adoption of remote work and more flexible work arrangements.

We modeled the telecommuting frequency model for Logan after the telecommuting frequency model in the SEMCOG model.
The SEMCOG model used variables such as the number of vehicles, the distance to work, income, worker status, gender, number of adults in the household, and the number of children in the household.

In our model for Logan, UT, we included a variety of alternative specific variables.
We included the life cycle of the household because individuals with young children may prefer to work from home or may need to work from home to take care of young children.
We also included the number of vehicles because the number of vehicles in a household may impact the ability of people in the household to commute which may impact the likelihood of working from home.
Income level was also included because the income of a person may affect their ability to have a home office and jobs in certain salary brackets may be more or less likely to have work from home options.
The final variable we included was the sex of the respondent because sex may also play a role in work location choices.

With these variables, we created multinomial logit models because the frequency at which individuals work from home may be different depending on these variables (@tbl-tc).
Unfortunately, even after much troubleshooting we are still getting a "computationally singular" error on many of these models, so only one is presented below.
This model will be revisited, but for now we are using this model as it is the only one we could get to work.

```{r echo = FALSE}
#| label: tbl-tc
#| tbl-cap: Telecommute frequency model estimates

modelsummary(
		tar_read(tc_models),
		estimate = "{estimate} ({p.value}){stars}",
		statistic = NULL,
		gof_omit = "r2|Num"
	)
```

## Auto Ownership

The auto ownership model is designed to analyze and predict the number of vehicles at each household.

We modeled the auto ownership model for Logan after the auto ownership model in the SEMCOG model.
The SEMCOG model used variables such as the number of drivers, the number of adults, the number of children, the income, the retail accessibility, and the auto time savings per worker to work.

In our model for Logan, UT, we included a variety of alternative specific variables.
We included the household income because the income of a household may affect the number of cars they can afford to have.
We also included the number of adults because the number of adults, assuming that they are also drivers, may affect the number of vehicles that they have in their household.
The number of workers was also included, for a similar reason to the number of adults.
The final variable we included was the number of workers in a household because the number of workers in a household may affect how many vehicles the household has in order to accommodate the workers.

We tried to analyze the difference between the number of vehicles and the number of adults as well as the difference between the number of vehicles and the number of workers.
Since we are trying to predict the number of vehicles, it did not work to use these differences as a generic variable because the differences are highly correlated with the number of vehicles in each household.

With these variables, we created several multinomial logit models because the number of vehicles for a given household may be different depending on these variables (@tbl-veho).
We will use Model 2 because it has many significant estimates and contains reasonable explanatory variables.

```{r echo = FALSE}
#| label: tbl-veho
#| tbl-cap: Vehicle ownership model estimates

modelsummary(
		tar_read(veho_models),
		estimate = "{estimate} ({p.value}){stars}",
		statistic = NULL,
		gof_omit = "r2|Num"
	) %>% 
	kable_styling(latex_options = "scale_down")
```

# Network

The network is taken from the production CUBE model for Cache County.
Currently, this network is in a bespoke format used in the CUBE model, and needs to be modified to work with AequilibraE.
This involves converting the node and link tables from the existing networm to the GMNS specification.
Some of this process is straightforward and has been completed, but we currently have no documentation on the CUBE model so some of the network data is unclear to us.
We have reached out to both UDOT and Fehr & Peers about this and are waiting to hear back from them.

Based on the experiences with the network and AequilibraE so far, this task is much more involved than previously thought.
Working network assignment and accessibility calculation steps will therefore need to be postponed to a future report.
