---
title: "Report 2"
metadata-files:
  - _metadata.yml
format: pdf
---

```{r}
#| include: false
library(tidyverse)
library(targets)
library(modelsummary)
library(kableExtra)
library(haven)
```

We have started a "deep clean" of the travel surveys.
Only minimal cleaning is required for many of the "long-term decision" ActivitySim models such as vehicle ownership and remote work status, and these models were estimated (preliminarily) previously.
However, the daily and tour- and trip-level models will require further cleaning of the travel surveys to properly estimate.

The first crucial step is to organize the survey trips into tours.
The Utah Household Travel Survey is already organized into tours, but not in the same manner as is needed for ActivitySim.
ActivitySim defines a tour as a set of trips beginning and ending at the home (with the exception of sub-tours; see below).
However, the Survey additionally "breaks" tours at work locations, so an individual may make a "Home-Work" tour which begins at home and ends at work.
For example, @fig-short-day shows the DAP of an individual that travels from home to work, school, a store, and back home.
In ActivitySim, this is considered a single tour, but the Survey counts this as two tours: a Home-Work tour and a Work-Home tour.

![]()

By contrast, @fig-home shows a DAP with several trips, but none are to work.
Both ActivitySim and the survey count this as a single tour; the Survey classifies this DAP as a Home-Home tour.

![]()

This is Report 2 which provides an update on Logan, UT activity-based travel model.

# Data Updates

## 

Cleaned up the reading in of the ut_hhts and the nhts Replaced the estimate_tc function with the one from Dr. Macfarlane's branch

## 

Started to clean the nhts_trips to identify tours

The different trip purposes: HBW = home based work NHBW = non-home based work HBPb = ??
HBO = home based other NHBNW = non-home based non-work HBSch = home based school HBShop = home based shop HBC = hoem based college?

```{r}

tar_load(ut_hhts)

unique(ut_hhts$trips$trip_pur_t)

ut_hhts$trips <- ut_hhts$trips %>% 
	filter(h_CO_NAME == "CACHE")

ggplot(ut_hhts$trips, aes(x = trip_pur_t)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Utah Household Travel Survey Trip Purposes",
       x = "Trip Purpose",
       y = "Frequency") +
  theme_bw()


# origin
# production
# destination
# home
# attraction
# work

```

```{r}
ut_hhts$trips <- ut_hhts$trips %>% 
	filter(h_CO_NAME == "CACHE")

unique(ut_hhts$trips$mode_t)

ggplot(ut_hhts$trips, aes(x = mode_t)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Utah Household Travel Survey Trip Modes",
       x = "Modes",
       y = "Frequency") +
  theme_bw()
```
