---
title: "Report 2"
metadata-files:
  - _metadata.yml
format: pdf
---

```{r echo = FALSE}
#| include: false
library(tidyverse)
library(targets)
library(modelsummary)
library(kableExtra)
library(haven)
```

This is Report 2 which provides an update on Logan, UT activity-based travel model.

# Data Updates

## 

Cleaned up the reading in of the ut_hhts and the nhts Replaced the estimate_tc function with the one from Dr. Macfarlane's branch

## 

Started to clean the nhts_trips to identify tours

The different trip purposes: HBW = home based work NHBW = non-home based work HBPb = ??
HBO = home based other NHBNW = non-home based non-work HBSch = home based school HBShop = home based shop HBC = hoem based college?

```{r, echo = FALSE}

tar_load(ut_hhts)

unique(ut_hhts$trips$trip_pur_t)

ut_hhts$trips <- ut_hhts$trips %>% 
	filter(h_CO_NAME == "CACHE")

ggplot(ut_hhts$trips, aes(x = trip_pur_t)) +
  geom_bar(fill = "skyblue", color = "black") +
  labs(title = "Utah Household Travel Survey Trip Purposes",
       x = "Trip Purpose",
       y = "Frequency") +
  theme_bw()


# origin
# production
# destination
# home
# attraction
# work

```
