---
title: "Report 3"
metadata-files:
  - _metadata.yml
format: pdf
---

```{r echo = FALSE}
#| include: false
library(tidyverse)
library(targets)
library(modelsummary)
library(kableExtra)
library(haven)
```

This report details the current state of the project.
We discuss the progress made in cleaning the Utah Household Travel Survey tour data.

# Survey Cleaning

In the previous report, we discussed our efforts as we began cleaning the Utah Household Travel Survey (UT HHTS).
The daily and tour- and trip-level models require further cleaning of the travel surveys to properly estimate.

## ActivitySim Tour Conversion

In the UT HHTS, each trip made by individuals is categorized.
There are eight different trip purposes.
These purposes are "HBC", "HBO", "HBPb", "HBShp", "HBW", "NHBNW", and "NHBW".
A distribution of these trips types is shown.

```{r}
tar_load(ut_hhts)

ggplot(ut_hhts$trips, aes(x = trip_pur_t)) +
	geom_bar(fill = "skyblue", color = "black") +
	labs(title = "UT HHTS Trip Purpose Frequency",
			 x = "Trip Purpose",
			 y = "Frequency") +
	theme_minimal()
```

Tours are made up of trips; tours are defined differently in the UT HHTS than they need to be defined in ActivitySim.

In the UT HHTS, there are five different tour types.
These are "Home-Home", "Home-Work", "Work-Home", "Work-Work", and "Incomplete".
The distribution of the tour types is shown.

```{r}
tar_load(ut_hhts)

ggplot(ut_hhts$trips, aes(x = TourType)) +
	geom_bar(fill = "skyblue", color = "black") +
	labs(title = "UT HHTS Tour Type Frequency",
			 x = "Tour Type",
			 y = "Frequency") +
	theme_minimal()
```

The "Home-Home" tours in the UT HHTS are tours that begin and end at home without any trips to work.
These tours already correctly designated to be used in ActivitySim and will be designated as "home" tours in ActivitySim.

The "Home-Work" and "Work-Home" trips need to be matched up to follow an individual from home to work and then from work back to home.
ActivitySim treats this as one tour, whereas the UT HHTS treats this as two tours.
Once these are matched up, they will be designed as "work" tours in ActivitySim.

The "Work-Work" tours are where an individual begins and ends trips at a work location.
If this "Work-Work" tour is travel from one work location to another, then ActivitySim should consider the sequence of trips to be part of the same main work tour of the given individual.
However, ActivitySim considers some of these "Work-Work" tours subtours, where a sequence of trips begins and ends at the same work location (such as going to lunch and returning to work).

In the UT HHTS, there are six different mode types.
These are "auto", "bike", "school bus", "transit", "walk", and "other".
The distribution of the mode types is shown.

```{r}
tar_load(ut_hhts)

ggplot(ut_hhts$trips, aes(x = mode_t)) +
	geom_bar(fill = "skyblue", color = "black") +
	labs(title = "UT HHTS Tour Type Frequency",
			 x = "Mode Type",
			 y = "Frequency") +
	theme_minimal()
```

